---
title: "Example on a simulated dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{run_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

We propose a simple example in which we apply SHIR to a generated dataset that mimicks data from M=4 sites. We show how to fit and derive summary data at each local site, and then aggregate the derived data. 
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load the library:
```{r setup}
library(SHIR)
```

Load the simulated dataset:
```{r}
data(simu_data)
```

The variables X are the individual covariates matrices, Y is the individual response vector:
```{r}
X_lst <- simu_data$X
Y_lst <- simu_data$Y
```

```{r echo = T, include = FALSE}
#parameters used for generating the data
n <- 400
p <- 400
```

Number of sites:
```{r}
M <- length(X_lst)
```

Vector for sample size of the local sites:
```{r}
length_lst <- c()
```

Initialize the lists of the derived hessian matrices, gradient vectors and lasso estimators respectively:
```{r}
I_lst <- vector('list', M)
U_lst <- vector('list', M)
beta_lst <- vector('list', M)
```

Locally fit and derive the individual data at site m:
```{r}
system.time(
for (m in 1:M){
  Y <- Y_lst[[m]]
  X <- X_lst[[m]]

  local_summary_m <- Local_fit(Y, X, lambda_lst = 0.1 * c(4:20) * sqrt((log(p)) / n))

  I_lst[[m]] <- local_summary_m$hessian
  U_lst[[m]] <- local_summary_m$gradient
  beta_lst[[m]] <- local_summary_m$beta
  length_lst <- c(length_lst, length(Y))
}
)
```

Aggregate the derived data:
```{r echo = T, results = 'hide'}
SHIR_train <- SHIR_fit(I_lst, U_lst, length_lst,
                       lambda_lst = sqrt(n * log(p)) * 0.3 * c(4:30),
                       lambda_g_lst = c(0.75, 1), tune = 'BIC')
```

# For convenience, one can also use the defaul parameters:
```{r echo = T, results = 'hide'}
SHIR_train <- SHIR_fit(I_lst, U_lst, length_lst)
```

Fitted beta. The m-th column loads the fitted beta for the m-th site, the first row displays the intercepts:
```{r}
head(SHIR_train$min.beta)
```

To obtain the fitted mean effect mu:
```{r}
head(rowMeans(SHIR_train$min.beta))
```

To obtain the fitted heterogeneous effect alpha (the m-th column loads alpha for the m-th site):
```{r}
head(SHIR_train$min.beta - rowMeans(SHIR_train$min.beta))
```
