---
title: "Toy Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{toy_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

We propose a simple example in which we apply SHIR to a generated dataset

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

load the library
```{r setup}
#library(SHIR)
```

load the simulated dataset
```{r , include = FALSE}
#simu_data <- load("https://raw.githubusercontent.com/celehs/SHIR/master/data-raw/dataSHIR.rda")
```

X are the individual covariates matrices, Y is the individual response vector
```{r , include = FALSE}
#X_lst <- simu_data$X
#Y_lst <- simu_data$Y
```

Fit and derive summary data at each local site:
```{r , include = FALSE}
# # number of sites:
# M <- length(X_lst)
# 
# # vector for sample size of the local sites:
# length_lst <- c()
# 
# # list for derived hessian matrices:
# I_lst <- vector('list', M)
# 
# # list for derived gradient vectors:
# U_lst <- vector('list', M)
# 
# # list for derived lasso estimators:
# beta_lst <- vector('list', M)
# 
# for (m in 1:M){
#   Y <- Y_lst[[m]]
#   X <- X_lst[[m]]
#   
#   # Locally fit and derive the individual data at site m:
#   
#   local_summary_m <- Local_fit(Y, X, lambda_lst = 0.1 * c(3:30) * sqrt((log(p)) / n))
#   
#   I_lst[[m]] <- local_summary_m$hessian
#   U_lst[[m]] <- local_summary_m$gradient
#   beta_lst[[m]] <- local_summary_m$beta
# }
```

Aggregate the derived data:
```{r , include = FALSE}
# SHIR_train <- SHIR_fit(I_lst, U_lst, length_lst, 
#                        lambda_lst = sqrt(n * log(p)) * 0.3 * c(5:30), 
#                        lambda_g_lst = sqrt(n * (log(p) + M)) * 0.3 * (5:30), 
#                        tune = 'BIC')
# 
# # Fitted beta (the m-th column loads the fitted beta for the m-th site, 
# #              the first row is the intercepts):
# 
# SHIR_train$min.beta
```

To obtain the fitted mean effect mu:
```{r , include = FALSE}
# rowMeans(SHIR_train$min.beta)
```

To obtain the fitted heterogeneous effect alpha (the m-th column loads alpha for the m-th site):
```{r , include = FALSE}
# SHIR_train$min.beta - rowMeans(SHIR_train$min.beta)
```
